Confirmation of \srcfull{} as a long period radio transient

### 2025-05-18 paper/main.tex
Switched from AASTeX to MNRAS templates

%% Beginning of file 'sample631.tex'
%%
%% Modified 2022 May  
%%
%% This is a sample manuscript marked up using the
%% AASTeX v6.31 LaTeX 2e macros.
%%
%% AASTeX is now based on Alexey Vikhlinin's emulateapj.cls 
%% (Copyright 2000-2015).  See the classfile for details.

%% AASTeX requires revtex4-1.cls and other external packages such as
%% latexsym, graphicx, amssymb, longtable, and epsf.  Note that as of 
%% Oct 2020, APS now uses revtex4.2e for its journals but remember that 
%% AASTeX v6+ still uses v4.1. All of these external packages should 
%% already be present in the modern TeX distributions but not always.
%% For example, revtex4.1 seems to be missing in the linux version of
%% TexLive 2020. One should be able to get all packages from www.ctan.org.
%% In particular, revtex v4.1 can be found at 
%% https://www.ctan.org/pkg/revtex4-1.

%% The first piece of markup in an AASTeX v6.x document is the \documentclass
%% command. LaTeX will ignore any data that comes before this command. The 
%% documentclass can take an optional argument to modify the output style.
%% The command below calls the preprint style which will produce a tightly 
%% typeset, one-column, single-spaced document.  It is the default and thus
%% does not need to be explicitly stated.
%%
%% using aastex version 6.3
\documentclass[preprint2,linenumbers]{aastex631}

\usepackage{amsmath}

%% The default is a single spaced, 10 point font, single spaced article.
%% There are 5 other style options available via an optional argument. They
%% can be invoked like this:
%%
%% \documentclass[arguments]{aastex631}
%% 
%% where the layout options are:
%%
%%  twocolumn   : two text columns, 10 point font, single spaced article.
%%                This is the most compact and represent the final published
%%                derived PDF copy of the accepted manuscript from the publisher
%%  manuscript  : one text column, 12 point font, double spaced article.
%%  preprint    : one text column, 12 point font, single spaced article.  
%%  preprint2   : two text columns, 12 point font, single spaced article.
%%  modern      : a stylish, single text column, 12 point font, article with
%%      wider left and right margins. This uses the Daniel
%%      Foreman-Mackey and David Hogg design.
%%  RNAAS       : Supresses an abstract. Originally for RNAAS manuscripts 
%%                but now that abstracts are required this is obsolete for
%%                AAS Journals. Authors might need it for other reasons. DO NOT
%%                use \begin{abstract} and \end{abstract} with this style.
%%
%% Note that you can submit to the AAS Journals in any of these 6 styles.
%%
%% There are other optional arguments one can invoke to allow other stylistic
%% actions. The available options are:
%%
%%   astrosymb    : Loads Astrosymb font and define \astrocommands. 
%%   tighten      : Makes baselineskip slightly smaller, only works with 
%%                  the twocolumn substyle.
%%   times        : uses times font instead of the default
%%   linenumbers  : turn on lineno package.
%%   trackchanges : required to see the revision mark up and print its output
%%   longauthor   : Do not use the more compressed footnote style (default) for 
%%                  the author/collaboration/affiliations. Instead print all
%%                  affiliation information after each name. Creates a much 
%%                  longer author list but may be desirable for short 
%%                  author papers.
%% twocolappendix : make 2 column appendix.
%%   anonymous    : Do not show the authors, affiliations and acknowledgments 
%%                  for dual anonymous review.
%%
%% these can be used in any combination, e.g.
%%
%% \documentclass[twocolumn,linenumbers,trackchanges]{aastex631}
%%
%% AASTeX v6.* now includes \hyperref support. While we have built in specific
%% defaults into the classfile you can manually override them with the
%% \hypersetup command. For example,
%%
%% \hypersetup{linkcolor=red,citecolor=green,filecolor=cyan,urlcolor=magenta}
%%
%% will change the color of the internal links to red, the links to the
%% bibliography to green, the file links to cyan, and the external links to
%% magenta. Additional information on \hyperref options can be found here:
%% https://www.tug.org/applications/hyperref/manual.html#x1-40003
%%
%% Note that in v6.3 "bookmarks" has been changed to "true" in hyperref
%% to improve the accessibility of the compiled pdf file.
%%
%% If you want to create your own macros, you can do so
%% using \newcommand. Your macros should appear before
%% the \begin{document} command.
%%
\newcommand{\vdag}{(v)^\dagger}
\newcommand\aastex{AAS\TeX}
\newcommand\latex{La\TeX}

@@

%% Reintroduced the \received and \accepted commands from AASTeX v5.2
%\received{March 1, 2021}
%\revised{April 1, 2021}
%\accepted{\today}

%% Command to document which AAS Journal the manuscript was submitted to.
%% Adds "Submitted to " the argument.
%\submitjournal{PSJ}

%% For manuscript that include authors in collaborations, AASTeX v6.31
%% builds on the \collaboration command to allow greater freedom to 
%% keep the traditional author+affiliation information but only show
%% subsets. The \collaboration command now must appear AFTER the group
%% of authors in the collaboration and it takes TWO arguments. The last
%% is still the collaboration identifier. The text given in this
%% argument is what will be shown in the manuscript. The first argument
%% is the number of author above the \collaboration command to show with
%% the collaboration text. If there are authors that are not part of any
%% collaboration the \nocollaboration command is used. This command takes
%% one argument which is also the number of authors above to show. A
%% dashed line is shown to indicate no collaboration. This example manuscript
%% shows how these commands work to display specific set of authors 
%% on the front page.
%%
%% For manuscript without any need to use \collaboration the 
%% \AuthorCollaborationLimit command from v6.2 can still be used to 
%% show a subset of authors.
%
%\AuthorCollaborationLimit=2
%
%% will only show Schwarz & Muench on the front page of the manuscript
%% (assuming the \collaboration and \nocollaboration commands are
%% commented out).
%%
%% Note that all of the author will be shown in the published article.
%% This feature is meant to be used prior to acceptance to make the
%% front end of a long author article more manageable. Please do not use
%% this functionality for manuscripts with less than 20 authors. Conversely,
%% please do use this when the number of authors exceeds 40.
%%
%% Use \allauthors at the manuscript end to show the full author list.
%% This command should only be used with \AuthorCollaborationLimit is used.

%% The following command can be used to set the latex table counters.  It
%% is needed in this document because it uses a mix of latex tabular and
%% AASTeX deluxetables.  In general it should not be needed.
%\setcounter{table}{1}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%% The following section outlines numerous optional output that
%% can be displayed in the front matter or as running meta-data.
%%
%% If you wish, you may supply running head information, although
%% this information may be modified by the editorial offices.
%\shorttitle{AASTeX v6.3.1 Sample article}
%\shortauthors{Schwarz et al.}
%%
%% You can add a light gray and diagonal water-mark to the first page 
%% with this command:
%% \watermark{text}
%% where "text", e.g. DRAFT, is the text to appear.  If the text is 
%% long you can control the water-mark size with:
%% \setwatermarkfontsize{dimension}
%% where dimension is any recognized LaTeX dimension, e.g. pt, in, etc.
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\graphicspath{{./}{figures/}}
%% This is the end of the preamble.  Indicate the beginning of the
%% manuscript itself with \begin{document}.

\begin{document}

\title{Confirmation of \srcfull{} as a long period radio transient}

%% LaTeX will automatically break titles if they run longer than
%% one line. However, you may use \\ to force a line break if
%% you desire. In v6.31 you can include a footnote in the title.

%% A significant change from earlier AASTEX versions is in the structure for 
%% calling author and affiliations. The change was necessary to implement 
%% auto-indexing of affiliations which prior was a manual process that could 
%% easily be tedious in large author manuscripts.
%%
%% The \author command is the same as before except it now takes an optional
%% argument which is the 16 digit ORCID. The syntax is:
%% \author[xxxx-xxxx-xxxx-xxxx]{Author Name}
%%
%% This will hyperlink the author name to the author's ORCID page. Note that
%% during compilation, LaTeX will do some limited checking of the format of
%% the ID to make sure it is valid. If the "orcid-ID.png" image file is 
%% present or in the LaTeX pathway, the OrcID icon will appear next to
%% the authors name.
%%
%% Use \affiliation for affiliation information. The old \affil is now aliased
%% to \affiliation. AASTeX v6.31 will automatically index these in the header.
%% When a duplicate is found its index will be the same as its previous entry.
%%
%% Note that \altaffilmark and \altaffiltext have been removed and thus 
%% can not be used to document secondary affiliations. If they are used latex
%% will issue a specific error message and quit. Please use multiple 
%% \affiliation calls for to document more than one affiliation.
%%
%% The new \altaffiliation can be used to indicate some secondary information
%% such as fellowships. This command produces a non-numeric footnote that is
%% set away from the numeric \affiliation footnotes.  NOTE that if an
%% \altaffiliation command is used it must come BEFORE the \affiliation call,
%% right after the \author command, in order to place the footnotes in
%% the proper location.
%%
%% Use \email to set provide email addresses. Each \email will appear on its
%% own line so you can put multiple email address in one \email call. A new
%% \correspondingauthor command is available in V6.31 to identify the
%% corresponding author of the manuscript. It is the author's responsibility
%% to make sure this name is also in the author list.
%%
%% While authors can be grouped inside the same \author and \affiliation
%% commands it is better to have a single author for each. This allows for
%% one to exploit all the new benefits and should make book-keeping easier.
%%
%% If done correctly the peer review system will be able to
%% automatically put the author and affiliation information from the manuscript
%% and save the corresponding author the trouble of entering it by hand.

%\correspondingauthor{August Muench}
%\email{greg.schwarz@aas.org, gus.muench@aas.org}

\author[0000-0001-6114-7469]{Samuel J. McSweeney}
\affiliation{International Centre for Radio Astronomy Research, Curtin University, Bentley, WA 6102, Australia}

\author[0000-0002-5119-4808]{Natasha Hurley-Walker}
\affiliation{International Centre for Radio Astronomy Research, Curtin University, Bentley, WA 6102, Australia}

\author{Dougal Dobie}
\affiliation{Sydney Institute for Astronomy, School of Physics, The University of Sydney, NSW 2006, Australia}
\affiliation{ARC Centre of Excellence for Gravitational Wave Discovery (OzGrav), Hawthorn, VIC 3122, Australia}

\author[0009-0003-0996-9176]{Csanad Horv\'{a}th}
\affiliation{International Centre for Radio Astronomy Research, Curtin University, Bentley, WA 6102, Australia}

\author{Angie Waszewski}
\affiliation{International Centre for Radio Astronomy Research, Curtin University, Bentley, WA 6102, Australia}

\author{John Morgan}
\affiliation{International Centre for Radio Astronomy Research, Curtin University, Bentley, WA 6102, Australia}

\author{Ziteng Wang}
\affiliation{International Centre for Radio Astronomy Research, Curtin University, Bentley, WA 6102, Australia}

%\collaboration{20}{(AAS Journals Data Editors)}

% Example with "altaffiliation"
%\author{Amy Hendrickson}
%\altaffiliation{AASTeX v6+ programmer}
%\affiliation{TeXnology Inc.}

%% Note that the \and command from previous versions of AASTeX is now
%% depreciated in this version as it is no longer necessary. AASTeX 
%% automatically takes care of all commas and "and"s between authors names.

%% AASTeX 6.31 has the new \collaboration and \nocollaboration commands to
%% provide the collaboration status of a group of authors. These commands 
%% can be used either before or after the list of corresponding authors. The
%% argument for \collaboration is the collaboration identifier. Authors are
%% encouraged to surround collaboration identifiers with ()s. The 
%% \nocollaboration command takes no argument and exists to indicate that
%% the nearby authors are not part of surrounding collaborations.

%% Mark off the abstract in the ``abstract'' environment. 
\begin{abstract}

  [Abstract goes here\dots]

\end{abstract}

%% Keywords should appear after the \end{abstract} command. 
%% The AAS Journals now uses Unified Astronomy Thesaurus concepts:
%% https://astrothesaurus.org
%% You will be asked to selected these concepts during the submission process
%% but this old "keyword" functionality is maintained in case authors want
%% to include these concepts in their preprints.
%\keywords{Classical Novae (251) --- Ultraviolet astronomy(1736) --- History of astronomy(1868) --- Interdisciplinary astronomy(804)}

%% From the front matter, we move on to the body of the paper.
%% Sections are demarcated by \section and \subsection, respectively.
%% Observe the use of the LaTeX \label
%% command after the \subsection to give a symbolic KEY to the
%% subsection for cross-referencing in a \ref command.
%% You can use LaTeX's \ref and \label commands to keep track of
%% cross-references to sections, equations, tables, and figures.
%% That way, if you change the order of any elements, LaTeX will
%% automatically renumber them.
%%
%% We recommend that authors also use the natbib \citep
%% and \citet commands to identify citations.  The citations are
%% tied to the reference list via symbolic KEYs. The KEY corresponds
%% to the KEY in the \bibitem in the reference list below.

@@

\begin{deluxetable*}{lllccc}
  \tablecaption{Observations summary\label{tbl:obs}}
  \tablehead{
    \colhead{Date range} & \colhead{Telescope} & Project & \colhead{$\nu$} & \colhead{$\Delta\nu$} & \colhead{Number of} \\ 
    \colhead{(MJD)} & & & \colhead{(MHz)} & \colhead{(MHz)} & \colhead{pulses}
  } 
  \startdata
  59965 & ASKAP\tablenotemark{a} & SB47253 & 887.5 & 288 & 1 \\
  59966 & MWA & G0060 & 161.92 & 15.36 & 1 \\
  %60084 & MWA & G0057 & 154.24 & 30.72 & $\le$ 1 \\
  60040  & ASKAP & SB49153 & 887.5 & 288 & 1 \\
  60092 - 60093 & MeerKAT & DDT-20230525-DD-01 & 1284 & 856 & 4 \\
  60463 - 60563 & MWA & G0080 & 200.32 & 30.72 & 16 \\
  60503 & ASKAP & SB63600 & 887.5 & 288 & 1 \\
  60572 & MWA & D0042 & 184.96 & 30.72 & 4 \\
  60592 - 60602 & MWA & D0042 & 200.32 & 30.72 & 17 \\
  60602 & MeerKAT & DDT-20241015-NH-01 & 812.8 & 495.3 & 1 \\
  \enddata
  \tablenotetext{a}{Original discovery \citepalias{2024MNRAS.535..909D}}
\end{deluxetable*}

@@

\begin{table}
  \caption{Timing ephemeris for \src{}}
  \label{tbl:ephemeris}
  \begin{tabular}{lc}
    \tableline
    Parameter & Value \\
    \tableline
    Period (s) & $4186.3283 \pm 0.0003$ \\
    PEPOCH (MJD) & $59965.03790 \pm 0.00003$ \\
    DM (pc/cm$^{-3}$) & $764 \pm 25$ \\
    $\tau_{\rm sc,1 GHz}$ (s) & ${\sim}0.07$\tablenotemark{a} \\
    \tableline
  \end{tabular}
 \tablenotetext{a}{Assumed value, degenerate with DM (see main text).}
\end{table}

@@

\src{}'s period and duty cycle are not dissimilar to ILT J1101+5521 and GLEAM-X J0704$-$37, which are confirmed polars (Fig. \ref{fig:lpt_comparison}), suggesting the possibility that \src{}, too, is a WD-MD polar system.
However, its period of ${\sim}1.16\,$hours would make it shorter than the minimum known orbital period of $1.3\,$hours for confirmed polars \citep{schwope2025polarcatcatalogpolarslowaccretion}.
This makes it an interesting testbed for the suggestion advanced by \citet{2025arXiv250103315R} that ``short LPTs'' ($P \lesssim 78\,$mins) and ``long LPTs'' ($P \gtrsim 78\,$mins) represent different classes of systems (AM CVns and CVs, respectively).
\begin{figure*}[th]
    \centering
    \includegraphics[width=0.98\linewidth]{lpt_comparison.pdf}
    \caption{Duty cycle vs radio pulse period for various classes of radio emitters. The duty cycles are derived from the reported pulse widths for LPTs, which are compared to the range of the fitted, unscattered pulse widths of \src{} at 10\% of the peak. AR\,Sco \citep{2016Natur.537..374M,2018A&A...611A..66S} and other sources without well-defined periods or duty cycles \citep[e.g.][and references therein]{2021ApJ...920...45W} are not included on this plot.
    \nocite{2024arXiv240707480D,2022Natur.601..526H,2023Natur.619..487H,2024NatAs...8.1159C,2005Natur.434...50H,2024arXiv240811536D,Lee2025}}
    \label{fig:lpt_comparison}
\end{figure*}

@@

\begin{acknowledgments}
 N.H.-W. is the recipient of an Australian Research Council Future Fellowship (project number FT190100231).

@@

\end{acknowledgments}

%% To help institutions obtain information on the effectiveness of their 
%% telescopes the AAS Journals has created a group of keywords for telescope 
%% facilities.
%
%% Following the acknowledgments section, use the following syntax and the
%% \facility{} or \facilities{} macros to list the keywords of facilities used 
%% in the research for the paper.  Each keyword is check against the master 
%% list during copy editing.  Individual instruments can be provided in 
%% parentheses, after the keyword, but they are not verified.

%\vspace{5mm}
%\facilities{HST(STIS), Swift(XRT and UVOT), AAVSO, CTIO:1.3m,
%CTIO:1.5m,CXO}

%% Similar to \facility{}, there is the optional \software command to allow 
%% authors a place to specify which programs were used during the creation of 
%% the manuscript. Authors should list each code and include either a
%% citation or url to the code inside ()s when available.

%\software{astropy \citep{2013A&A...558A..33A,2018AJ....156..123A},  
%          Cloudy \citep{2013RMxAA..49..137F}, 
%          Source Extractor \citep{1996A&AS..117..393B}
%          }

%% Appendix material should be preceded with a single \appendix command.
%% There should be a \section command for each appendix. Mark appendix
%% subsections with the same markup you use in the main body of the paper.

%% Each Appendix (indicated with \section) will be lettered A, B, C, etc.
%% The equation counter will reset when it encounters the \appendix
%% command and will number appendix equations (A1), (A2), etc. The
%% Figure and Table counter will not reset.

@@

We confirm the order of magnitude of the above results by reporting a measured in-band DM for one of the MWA pulses at 185\,MHz, using the TMPL method to measure ToAs in 1.28\,MHz subbands from ${\sim}170$ to ${\sim}200\,$MHz, of ${\rm DM}_{\rm in-band} = 1221\pm257\,$pc\,cm$^{-3}$.
This exceeds the DM reported in this work by ${\sim}450\,$pc\,cm$^{-3}$, in excess of the prediction shown in panel (d), but consistent within measurement errors.

\bibliography{biblio}{}
\bibliographystyle{aasjournal}

%% This command is needed to show the entire author+affiliation list when
%% the collaboration and author truncation commands are used.  It has to
%% go at the end of the manuscript.
%\allauthors

%% Include this line if you are using the \added, \replaced, \deleted
%% commands to see a summary list of all changes at the end of the article.
%\listofchanges

\end{document}

% End of file `sample631.tex'.

>>>>

% mnras_template.tex 
%
% LaTeX template for creating an MNRAS paper
%
% v3.3 released April 2024
% (version numbers match those of mnras.cls)
%
% Copyright (C) Royal Astronomical Society 2015
% Authors:
% Keith T. Smith (Royal Astronomical Society)

% Change log
%
% v3.3 April 2024
%   Updated \pubyear to print the current year automatically
% v3.2 July 2023
%	Updated guidance on use of amssymb package
% v3.0 May 2015
%    Renamed to match the new package name
%    Version number matches mnras.cls
%    A few minor tweaks to wording
% v1.0 September 2013
%    Beta testing only - never publicly released
%    First version: a simple (ish) template for creating an MNRAS paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Basic setup. Most papers should leave these options alone.
\documentclass[fleqn,usenatbib]{mnras}

% MNRAS is set in Times font. If you don't have this installed (most LaTeX
% installations will be fine) or prefer the old Computer Modern fonts, comment
% out the following line
\usepackage{newtxtext,newtxmath}
% Depending on your LaTeX fonts installation, you might get better results with one of these:
%\usepackage{mathptmx}
%\usepackage{txfonts}

% Use vector fonts, so it zooms properly in on-screen viewing software
% Don't change these lines unless you know what you are doing
\usepackage[T1]{fontenc}

% Allow "Thomas van Noord" and "Simon de Laguarde" and alike to be sorted by "N" and "L" etc. in the bibliography.
% Write the name in the bibliography as "\VAN{Noord}{Van}{van} Noord, Thomas"
\DeclareRobustCommand{\VAN}[3]{#2}
\let\VANthebibliography\thebibliography
\def\thebibliography{\DeclareRobustCommand{\VAN}[3]{##3}\VANthebibliography}

%%%%% AUTHORS - PLACE YOUR OWN PACKAGES HERE %%%%%

% Only include extra packages if you really need them. Avoid using amssymb if newtxmath is enabled, as these packages can cause conflicts. newtxmatch covers the same math symbols while producing a consistent Times New Roman font. Common packages are:
\usepackage{graphicx}	% Including figure files
\usepackage{amsmath}	% Advanced maths commands

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%% AUTHORS - PLACE YOUR OWN COMMANDS HERE %%%%%

% Please keep new commands to a minimum, and use \newcommand not \def to avoid
% overwriting existing commands. Example:
%\newcommand{\pcm}{\,cm$^{-2}$}	% per cm-squared

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%%%%%

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[Confirmation of \src{} as LPT]{Confirmation of \srcfull{} as a long period radio transient}

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[S. J. McSweeney et al.]{
Samuel J. McSweeney,$^{1}$
Natasha Hurley-Walker,$^{1}$
Dougal Dobie$^{2,3}$
Csanad Horv\'{a}th$^{1}$
Angie Waszewski$^{1}$
John Morgan$^{1}$
and Ziteng Wang$^{1}$
\\
% List of institutions
$^{1}$International Centre for Radio Astronomy Research, Curtin University, Bentley, WA 6102, Australia\\
$^{2}$Sydney Institute for Astronomy, School of Physics, The University of Sydney, NSW 2006, Australia\\
$^{3}$ARC Centre of Excellence for Gravitational Wave Discovery (OzGrav), Hawthorn, VIC 3122, Australia
}

% These dates will be filled out by the publisher
\date{Accepted XXX. Received YYY; in original form ZZZ}

% Prints the current year, for the copyright statements etc. To achieve a fixed year, replace the expression with a number. 
\pubyear{\the\year{}}

% Don't change these lines
\begin{document}
\label{firstpage}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\maketitle

% Abstract of the paper
\begin{abstract}
\dots
\end{abstract}

% Select between one and six entries from the list of approved keywords.
% Don't make up new ones.
\begin{keywords}
radio continuum: transients -- white dwarfs
\end{keywords}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%% BODY OF PAPER %%%%%%%%%%%%%%%%%%

@@

\begin{table*}
  \centering
  \caption{Observations summary}
  \label{tbl:obs}
  \begin{tabular}{lllccc}
    \hline
    Date range & Telescope & Project & $\nu$ & $\Delta\nu$ & Number of \\ 
    (MJD) & & & (MHz) & (MHz) & pulses \\
    \hline 
    59965 & ASKAP & SB47253 (original discovery) & 887.5 & 288 & 1 \\
    59966 & MWA & G0060 & 161.92 & 15.36 & 1 \\
    %60084 & MWA & G0057 & 154.24 & 30.72 & $\le$ 1 \\
    60040  & ASKAP & SB49153 & 887.5 & 288 & 1 \\
    60092 - 60093 & MeerKAT & DDT-20230525-DD-01 & 1284 & 856 & 4 \\
    60463 - 60563 & MWA & G0080 & 200.32 & 30.72 & 16 \\
    60503 & ASKAP & SB63600 & 887.5 & 288 & 1 \\
    60572 & MWA & D0042 & 184.96 & 30.72 & 4 \\
    60592 - 60602 & MWA & D0042 & 200.32 & 30.72 & 17 \\
    60602 & MeerKAT & DDT-20241015-NH-01 & 812.8 & 495.3 & 1 \\
    \hline
  \end{tabular}
\end{table*}

@@

\begin{table}
  \centering
  \caption{Timing ephemeris for \src{}}
  \label{tbl:ephemeris}
  \begin{tabular}{lc}
    \hline
    Parameter & Value \\
    \hline
    Period (s) & $4186.3283 \pm 0.0003$ \\
    PEPOCH (MJD) & $59965.03790 \pm 0.00003$ \\
    DM (pc/cm$^{-3}$) & $764 \pm 25$ \\
    $\tau_{\rm sc,1 GHz}$ (s) & ${\sim}0.07$ \\
    \hline
  \end{tabular}
\end{table}

@@

\src{}'s period and duty cycle are not dissimilar to ILT J1101+5521 and GLEAM-X J0704$-$37, which are confirmed polars (Fig. \ref{fig:lpt_comparison}), suggesting the possibility that \src{}, too, is a WD-MD polar system.
However, its period of ${\sim}1.16\,$hours would make it shorter than the minimum known orbital period of $1.3\,$hours for confirmed polars \citep{schwope2025polarcatcatalogpolarslowaccretion}.
This makes it an interesting testbed for the suggestion advanced by \citet{2025arXiv250103315R} that ``short LPTs'' ($P \lesssim 78\,$mins) and ``long LPTs'' ($P \gtrsim 78\,$mins) represent different classes of systems (AM CVns and CVs, respectively).
\begin{figure*}[th]
    \centering
    \includegraphics[width=0.98\linewidth]{lpt_comparison.pdf}
    \caption{Duty cycle vs radio pulse period for various classes of radio emitters \citep{2024arXiv240707480D,2022Natur.601..526H,2023Natur.619..487H,2024NatAs...8.1159C,2005Natur.434...50H,2024arXiv240811536D,Lee2025}. The duty cycles are derived from the reported pulse widths for LPTs, which are compared to the range of the fitted, unscattered pulse widths of \src{} at 10\% of the peak. AR\,Sco \citep{2016Natur.537..374M,2018A&A...611A..66S} and other sources without well-defined periods or duty cycles \citep[e.g.][and references therein]{2021ApJ...920...45W} are not included on this plot.}
    \label{fig:lpt_comparison}
\end{figure*}

@@

\section*{Acknowledgements}

N.H.-W. is the recipient of an Australian Research Council Future Fellowship (project number FT190100231).

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Data Availability}

\dots

%The inclusion of a Data Availability Statement is a requirement for articles published in MNRAS. Data Availability Statements provide a standardised format for readers to understand the availability of data underlying the research results described in the article. The statement may refer to original data generated in the course of the study or to third-party data analysed in the article. The statement should describe and provide means of access, where possible, by linking to the data or providing the required accession numbers for the relevant databases or DOIs.

%%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%

% The best way to enter references is to use BibTeX:

\bibliographystyle{mnras}
\bibliography{biblio} % if your bibtex file is called example.bib

% Alternatively you could enter them by hand, like this:
% This method is tedious and prone to error if you have lots of references
%\begin{thebibliography}{99}
%\bibitem[\protect\citeauthoryear{Author}{2012}]{Author2012}
%Author A.~N., 2013, Journal of Improbable Astronomy, 1, 1
%\bibitem[\protect\citeauthoryear{Others}{2013}]{Others2013}
%Others S., 2012, Journal of Interesting Stuff, 17, 198
%\end{thebibliography}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%% APPENDICES %%%%%%%%%%%%%%%%%%%%%

@@

We confirm the order of magnitude of the above results by reporting a measured in-band DM for one of the MWA pulses at 185\,MHz, using the TMPL method to measure ToAs in 1.28\,MHz subbands from ${\sim}170$ to ${\sim}200\,$MHz, of ${\rm DM}_{\rm in-band} = 1221\pm257\,$pc\,cm$^{-3}$.
This exceeds the DM reported in this work by ${\sim}450\,$pc\,cm$^{-3}$, in excess of the prediction shown in panel (d), but consistent within measurement errors.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Don't change these lines
\bsp	% typesetting comment
\label{lastpage}
\end{document}

% End of mnras_template.tex
